### 2013-07-31 1_introduction/introduction_ivm.tex
Final changes before submission to Alan???

%Given the BIG problem, Why it is important to solve this problem?
The
                big picture, as introduced above, is that POLSAR data is multi­dimensional,
                stochastic, multiplicative and heteroskedastic.
%Under
%                this context, the motivation is to gain a better
%                understanding of the data,
%which
%                hopefully will lead to better information that can be
%                extracted from these data.
Under this condition, it is very important to understand the statistical models for SAR
data. It is these models that form the foundation for different SAR data processing
techniques, for example speckle filtering, target detection, image segmentation, and
other clustering, classification techniques.
In fact, due to the random nature of speckle, all of these techniques are essentially based on statistical estimation theory,
which comprises statistical modeling and validation, estimator design and development
as well as evaluation of different estimators’ accuracy. And central to this statistical
estimation theory is the need for statistically consistent discrimination measures which
are commonly derived from the statistical models.

That is, while different statistical models have been developed for different POLSAR
observables, for a statistical model to be useful, scalar discrimination measures need to
be derived from it. At the same time, the extension from SAR to POLSAR brings about
a representation difficulty in that: there exists not one, like the intensity in SAR, but
many observable quantities in POLSAR. Thus on the one hand, practical application for
POLSAR data processing requires the measure to be scalar, consistent and preferably
homoskedastic. On the other hand, the observable quantity being modeled needs to
be naturally representative of the high dimensional POLSAR data.

%Solving these dual-problem is both important and interesting.
%The statistical models are undoubtedly important in understanding the stochastic nature of the data. 
%At the same time, the statistical properties of the input data set greatly affect the choice and the performance of information extraction and statistical estimation techniques.
In addition, most of these data processing techniques are traditionally designed for additive and homoskedastic data.
In fact, unless proven otherwise, it is both convenient and acceptable to assume that the additive white noise model is appropriate for any given set of data samples.
This is due to a number of reasons, for example the prevalence of the normal distribution which results from the central limit theorem, or the prevalence of the additive noise model which probably arises due to the linear and additive nature of digital data. % dear Ian I changed this back 
%of the Additive White Gaussian Noise (AWGN) model in natural processes.
%of the additive noise model which probably arises due to the linear and additive nature of digital data.%****IVM I'm not sure about this - you seem to assume (in this sentence) that digital data is linear and additive. However this is definitely not true - your POLSAR data is digital and yet is not additive. Maybe you can say "or the prevalence of AWGN in the majority of sensing or sampling systems, and electronic devices."
%OR PERHAPS THIS: "... the prevalence of AWGN in natural processes."
It should be noted that even for the case of SAR data which is digital and not additive,
  the above statement is still true as SAR actually has two components, real and imaginary part,
  and all of them follows the standard Additive White Gaussian Noise model.

Both SAR and POLSAR data however is multiplicative and heteroskedastic by nature.
While there is no doubt that a number of data processing techniques have been proposed to handle certain aspects of the data, the breadth and depth of these studies trails in comparison to that of the more familiar additive and homoskedastic model.
This leads to the fact that a lot of times, existing statistical or computational techniques initially designed for additive and homoskedastic models are applied on multiplicative and heteroskedastic data, in ignorance of the incompatibility. 
An example is the use of mean, variance and squared error criteria, which are linear by nature and works excellently on additive and homoskedastic models, being applied on multiplicative and heteroskedastic distribution such as the gamma distribution.
Such use, however, is known to be not very robust for these so-called heavy tailed distributions.

Similarly speaking, heteroskedasticity poses numerous negative impacts on the usual framework of statistical estimation, which most of the time makes use of various different techniques and criteria known to work very well on the usual models.
For example, in modelling, it is very common to use subtractive differences to discriminate and to make decisional inferences. However for heteroskedastic SAR, it is known that such use should be avoided in preference to a ratio-based discrimination measure.
Another example is in the normal performance evaluation stage of statistical estimators, where the Ordinary Least Square (OLS) is widely used as the best evaluation criteria which is probably due to the Gauss Markov theorem.
For SAR data, however, its heteroskedasticity directly violates the homoskedastic assumption of the theorem and thus many different ways to evaluate SAR speckle filters were proposed.

@@

%How do others solve this problem?
%Briefly What are their solution? what problems they cannot yet solve?
While
                the statistical model for SAR is quite well understood,
the
                understanding of the POLSAR statistical model trails behind.
The
                complex POLSAR data have been statistically modelled as
                following the complex Wishart distribution, which
                apparently is multi­dimensional, complex and
                un­intuitive.
There
                has been a few published scalar statistical models for
                POLSAR, but none of them fit the dual criteria of being
                highly representative of the data and at the same time
                lead to scalar discrimination measures.
There
                are also a few POLSAR discrimination measures proposed,
                but all of them are based on the likelihood test
                statistics, which so far have only shown to be based on an
                asymptotic distribution.

 In
                another thread of study, to combat the negative
                impacts caused by multiplicative and heteroskedastic
                properties for SAR data, experienced researchers of the
                field have developed numerous ingenious ways to tackle
                these issues.
For
                example, when the sense of subtractive distance is not
                consistent for SAR data, the ratio is proposed as its
                discrimination measure \cite{Rignot_1993_TGRS_896}.
Or
                when the MMSE criteria is not very suitable to evaluate
                SAR speckle filters, other criteria likes radiometric
                preservation and speckle suppression power evaluation
                are employed. 
Unfortunately,
                these counter­intuitive measures are not very popular
                outside the SAR community, and newcomers to the field
                are frequently found being trapped in these pitfalls.

@@

 Another
                novelty of the contributions in this thesis comes from the systematic
                treatment towards the problem of statistical estimation
                of heteroskedastic SAR data.
While
                many different ways to combat the negative impacts
                caused by multiplicative and heteroskedastic properties
                for SAR data have been proposed over the years, they have often been
                handled in a piecemeal manner.
Here,
                a systematic homoskedastic framework of statistical
                estimation is developed, where not only homoskedastic
                statistical models are proposed, the impacts of
                homoskedasticity on estimator development and
                performance evaluation of statistical estimators is also
                studied.
This
                comprehensive treatment not only explains why the
                original SAR data requires special treatment very
                different to the common practice of computational
                sciences, 
it
                also allows thorough and unique discussion, for example on
                evaluating different evaluation criteria for statistical
                estimators.  % ;-)).
And
                since the POLSAR data can be considered as the multi
                dimensional extension of traditional SAR data, these
                treatments are shown extensible towards POLSAR data
                which is definitely yet another novelty.

%precise problem statement
With this approach, the \textbf{main problem statement} of this thesis arise. %it is important to emphasize again the main problem statement of this thesis.
That is
                this thesis focuses on providing a solution for the
                dual-problem of: 1) establishing scalar and
                representative statistical models for the
                multi-dimensional and inter-correlated POLSAR data and
                2) providing consistent measures of distance for both
                SAR and POLSAR data which allow the benefits of the
                homoskedastic statistical estimation framework to be
                demonstrated.

@@

The
                development of these models are based on
                rigorous statistical mathematics transformations. % and theory. 
The
                assumptions used are minimal and widely
                acknowledged for this type of data.
Then, the variable change theorem is applied to derive the statistical model for these transformed observables. %log-transformed SAR data.
The
                derived theoretical models are validated against
                real life data.
And
                the imperfect conditions found in practice (in
                comparison to the theoretical assumption) are also
                investigated, and the models are shown to be robust, capable of
                handling these imperfections.
The
                theoretical properties of these models, as well as many
                of their benefits, are also proven using rigorous
                mathematical principles.

@@

%How do you evaluate your solution? 
The
                achievement of the research objectives stated above not only provides
                novel solutions to the stated problem, it also
                illustrates the advantages and beneficial implications
                of the proposed theory.  
Compared
                to existing published techniques, the advantage of the
                proposed theory is qualitative, which does not require
                direct quantitative comparisons.
Instead
                a straightforward binary evaluation would be sufficient.
For
                the POLSAR scalar model, its advantages are that not
                only does it lead to consistent discrimination measures, it
                also generalizes the traditional model for one
                dimensional SAR intensity.
For
                the homoskedastic models, their advantage is that they
                enable an additive and homoskedastic statistical
                framework, which is not only capable of overcome various
                negative impacts of heteroskedasticity, but also results
                in a single better evaluation criteria that can combine
                and represent many different existing performance
                criteria.

@@

To evaluate the models’ application in statistical estimation framework, a practical point of view is adopted.
Practically, all estimators would eventually need to be applied on and work for real images.
Contrary to experiments on simulated data, experiments on real images often can only be compared qualitatively.
This however is critical and will always be included in our investigations.
The reason is that this helps to guard against any systematic errors in the various assumptions and approximations made in developing the theoretical models.
Towards that end, real-data can help to build and validate statistical models.

\section{Research Contributions}
% How do you know if the problem is solved?   State your research objectives
Interestingly, the dual-problem stated above are found to have a single solution.
They are the derivation of scalar, representative and homoskedastic measures of distance for the POLSAR data
  which is multidimensional, inter-correlated and heteroskedastic

Specifically, the following sub-objectives are to be achieved
\begin{enumerate}
\item                 To derive scalar and representative statistical models
                for the multi-dimensional and inter-correlated POLSAR
                data.
                \begin{enumerate}
                \item \label{itm:polsar_model} To derive a scalar statistical model for the
                POLSAR observable, being the determinant of the
                covariance matrix.
                \item \label{itm:polsar_discrimination_measure} To derive consistent discrimination measures for
                the observable being modeled 
                \item \label{itm:polsar_include_sar} To illustrate its representation power by showing
                that when the multi-channel POLSAR data is collapsed
                into the traditional one-channel SAR data, this
                determinant is transformed into the representative SAR
                intensity.
                \item \label{itm:polsar_validation} To validate the model against practical real-life
                captured POLSAR data.
                \item \label{itm:extend_sar_to_polsar} To demonstrate an example where an existing SAR
                processing technique is extensible towards POLSAR data
                \end{enumerate}
\item                To derive homoskedastic statistical models for the
                heteroskedastic (POL)SAR data. 
                \begin{enumerate}
                \item \label{itm:log_transform} To show that (POL)SAR data are heteroskedastic in
                the original domain and logarithmic transformation
                can convert this into a homoskedastic model.
                \item \label{itm:sar_measures_distance} To derive homoskedastic measures of distance for
                the multi dimensional POLSAR as well as for the one
                dimensional SAR data.
                \item \label{itm:sar_validation} To validate these statistical models against both
                practical SAR and POLSAR data
                \item To illustrate the beneficial applications of these
                statistical models. Specifically:
                \begin{enumerate}
                \item \label{itm:filter_vicious_circle} To show how the consistent sense of variance
                helps break the vicious cycle in the problem of SAR
                speckle filtering: a new statistical test for
                homogeneity and a new speckle filter is derived.
                \item \label{itm:log_mse} To show how the consistent sense of subtractive
                distance helps in the problem of evaluating (POL)SAR
                speckle filters: the log-MSE is proposed to combine the
                evaluation of radiometric preservation and speckle
                suppression power.
                \end{enumerate}
                \end{enumerate}
\end{enumerate}

@@

\section{Organisation of the Thesis}
The rest of this thesis is organized into five chapters, as follows:
The next chapter will survey the related publications
  and state-of-the-art techniques in modelling, processing, filtering and evaluating (POL)SAR speckle filter will be presented.
It will also discuss the different measures of distance for both SAR and POLSAR data, together with their extensive applications. 
Through these discussion, the need for a homoskedastic and scalar model for the multivariate and heteroskedastic POLSAR is brought forward.

@@

 The
                beneficial applications of these models is presented in
                chapter \ref{chap:applications}, where the consistent sense of variance
                property helps to break the vicious cycle in SAR
                speckle filtering (Research Contribution \ref{itm:filter_vicious_circle}).
It
                also shows how MSE can be again applicable in the
                additive and homoskedastic domain to evaluate SAR
                speckle filters (Research Contribution \ref{itm:log_mse}).
An
                example of extending existing techniques from SAR to
                POLSAR is also demonstrated in this chapter where the
                MSE evaluation criteria is also shown capable of
                evaluating POLSAR speckle filters (Research Contribution \ref{itm:extend_sar_to_polsar}).
Finally, the contribution of the thesis with respect to the research objectives and research impact is discussed in the concluding chapter \ref{chap:conclusions}.

>>>>

%Given the BIG problem, Why it is important to solve this problem?
The
                big picture, as introduced above, is that POLSAR data is multi-dimensional,
                stochastic, multiplicative and heteroskedastic.
%Under
%                this context, the motivation is to gain a better
%                understanding of the data,
%which
%                hopefully will lead to better information that can be
%                extracted from these data.
Under this condition, it is very important to understand the statistical models for SAR
data. It is these models that form the foundation for different SAR data processing
techniques, for example speckle filtering, target detection, image segmentation, and
other clustering, classification techniques.
In fact, due to the random nature of speckle, all of these techniques are essentially based on statistical estimation theory,
which comprises statistical modelling and validation, estimator design and development
as well as evaluation of different estimators' accuracy. And central to this statistical
estimation theory is the need for statistically consistent discrimination measures which
are commonly derived from the statistical models.

That is, while different statistical models have been developed for different POLSAR
observables, for a statistical model to be useful, scalar discrimination measures need to
be derived from it. At the same time, the extension from SAR to POLSAR brings about
a representation difficulty in that: there exists not one, like the intensity in SAR, but
many observable quantities in POLSAR. Thus, on the one hand, practical applications for
POLSAR data processing require measures which are scalar, consistent and preferably
homoskedastic. On the other hand, the observable quantity being modelled needs to
be naturally representative of the high dimensional POLSAR data.

%Solving these dual-problem is both important and interesting.
%The statistical models are undoubtedly important in understanding the stochastic nature of the data. 
%At the same time, the statistical properties of the input data set greatly affect the choice and the performance of information extraction and statistical estimation techniques.
In addition, most of these data processing techniques are traditionally designed for additive and homoskedastic data.
In fact, unless proven otherwise, it is both convenient and acceptable to assume that the additive white noise model is appropriate for any given set of data samples.
This is due to a number of reasons, for example the prevalence of the normal distribution which results from the central limit theorem, or the prevalence of the additive noise model which probably arises due to the linear and additive nature of digital data. % dear Ian I changed this back 
%of the Additive White Gaussian Noise (AWGN) model in natural processes.
%of the additive noise model which probably arises due to the linear and additive nature of digital data.%****IVM I'm not sure about this - you seem to assume (in this sentence) that digital data is linear and additive. However this is definitely not true - your POLSAR data is digital and yet is not additive. Maybe you can say "or the prevalence of AWGN in the majority of sensing or sampling systems, and electronic devices."
%OR PERHAPS THIS: "... the prevalence of AWGN in natural processes."
%****IVM2: I'm still not sure about it, but we can put it to the examiner, see if he picks it up.
It should be noted that even for the case of SAR data which is digital and not additive,
  the above statement is still true as SAR actually has two components, the real and imaginary parts,
  both of which follow the standard Additive White Gaussian Noise model.
%****IVM: I really don't understand what you're trying to say here.  Are you saying that "both parts are corrupted by AWGN"?

Both SAR and POLSAR data however are multiplicative and heteroskedastic by nature.
While there is no doubt that a number of data processing techniques have been proposed to handle certain aspects of the data, the breadth and depth of these studies trails in comparison to that of the more familiar additive and homoskedastic model.
This leads to the fact that a lot of times, existing statistical or computational techniques initially designed for additive and homoskedastic models are applied on multiplicative and heteroskedastic data, in ignorance of the incompatibility. 
An example is the use of mean, variance and squared error criteria, which are linear by nature and work excellently on additive and homoskedastic models, being applied on multiplicative and heteroskedastic distribution such as the gamma distribution.
Such use, however, is known to be not very robust for these so-called heavy tailed distributions.

Similarly speaking, heteroskedasticity poses numerous negative impacts on the usual framework of statistical estimation, which most of the time makes use of various different techniques and criteria known to work very well on the usual models.
For example, in modelling, it is very common to use subtractive differences to discriminate and to make decisional inferences. However, for heteroskedastic SAR, it is known that such use should be avoided in preference to a ratio-based discrimination measure.
Another example is in the normal performance evaluation stage of statistical estimators, where the Ordinary Least Square (OLS) is widely used as the best evaluation criteria which is probably due to the Gauss Markov theorem.
For SAR data, however, its heteroskedasticity directly violates the homoskedastic assumption of the theorem and thus many different ways to evaluate SAR speckle filters were proposed.

@@

%How do others solve this problem?
%Briefly What are their solution? what problems they cannot yet solve?
While
                the statistical model for SAR is quite well understood,
the
                understanding of the POLSAR statistical model trails behind.
The
                complex POLSAR data have been statistically modelled as
                following the complex Wishart distribution, which
                apparently is multi-dimensional, complex and
                un-intuitive.
There
                have been a few published scalar statistical models for
                POLSAR, but none of them fit the dual criteria of being
                highly representative of the data and at the same time
                lead to scalar discrimination measures.
There
                are also a few POLSAR discrimination measures proposed,
                but all of them are based on the likelihood test
                statistics, which so far have only shown to be based on an
                asymptotic distribution.

 In
                another thread of study, to combat the negative
                impacts caused by multiplicative and heteroskedastic
                properties for SAR data, experienced researchers in the
                field have developed numerous ingenious ways to tackle
                these issues.
For
                example, when the sense of subtractive distance is not
                consistent for SAR data, the ratio is proposed as its
                discrimination measure \cite{Rignot_1993_TGRS_896}.
Or
                when the MMSE criteria is not very suitable to evaluate
                SAR speckle filters, other criteria likes radiometric
                preservation and speckle suppression power evaluation
                are employed. 
Unfortunately,
                these counter-intuitive measures are not very popular
                outside the SAR community, and newcomers to the field
                are frequently found being trapped by these pitfalls.

@@

 Another
                novelty of the contributions in this thesis comes from the systematic
                treatment towards the problem of statistical estimation
                of heteroskedastic SAR data.
While
                many different ways to combat the negative impacts
                caused by multiplicative and heteroskedastic properties
                for SAR data have been proposed over the years, they have often been
                handled in a piecemeal manner.
Here,
                a systematic homoskedastic framework of statistical
                estimation is developed, where not only homoskedastic
                statistical models are proposed, the impacts of
                homoskedasticity on estimator development and
                performance evaluation of statistical estimators is also
                studied.
This
                comprehensive treatment not only explains why the
                original SAR data requires special treatment very
                different to the common practice of computational
                sciences, 
it
                also encourages a thorough and unique discussion, for example on
                evaluating different evaluation criteria for statistical
                estimators.  % ;-)).
And
                since the POLSAR data can be considered as the multi
                dimensional extension of traditional SAR data, these
                treatments are shown extensible towards POLSAR data
                which is definitely yet another novelty.

%precise problem statement
With this approach, the \textbf{main problem statement} of this thesis arises. %it is important to emphasize again the main problem statement of this thesis.
That is,
                this thesis focuses on providing a solution for the
                dual-problem of: 1) establishing scalar and
                representative statistical models for the
                multi-dimensional and inter-correlated POLSAR data and
                2) providing consistent measures of distance for both
                SAR and POLSAR data which allow the benefits of the
                homoskedastic statistical estimation framework to be
                demonstrated.

@@

The
                development of these models are based on
                rigorous statistical mathematics transformations. % and theory. 
The
                assumptions used are minimal and widely
                acknowledged for this type of data.
Then, the variable change theorem is applied to derive the statistical model for these transformed observables. %log-transformed SAR data.
The
                derived theoretical models are validated against
                real life data.
The
                imperfect conditions found in practice (in
                comparison to the theoretical assumptions) are also
                investigated, and the models are shown to be robust, capable of
                handling these imperfections.
The
                theoretical properties of these models, as well as many
                of their benefits, are also proven using rigorous
                mathematical principles.

@@

%How do you evaluate your solution? 
The
                achievement of the research objectives stated above not only provides
                novel solutions to the stated problem, it also
                illustrates the advantages and beneficial implications
                of the proposed theory.  
Compared
                to existing published techniques, the advantage of the
                proposed theory is qualitative, which does not require
                direct quantitative comparisons.
Instead
                a straightforward binary evaluation would be sufficient.
For
                the POLSAR scalar model, its advantages are that not
                only does it lead to consistent discrimination measures, it
                also generalizes the traditional model for one
                dimensional SAR intensity.
For
                the homoskedastic models, their advantage is that they
                enable an additive and homoskedastic statistical
                framework, which is not only capable of overcoming various
                negative impacts of heteroskedasticity, but also results
                in a single better evaluation criteria that can combine
                and represent many different existing performance
                criteria.

@@

To evaluate the application of these models in a statistical estimation framework, a practical point of view is adopted.
Practically, all estimators would eventually need to be applied on and work for real images.
Contrary to experiments on simulated data, experiments on real images can often only be compared qualitatively.
This however is critical and will always be included in our investigations.
The reason is that this helps to guard against any systematic errors in the various assumptions and approximations made in developing the theoretical models.
Towards that end, real-data can help to build and validate statistical models.

\section{Research Contributions}
% How do you know if the problem is solved?   State your research objectives
Interestingly, the dual-problems stated above are found to have a single solution.
They are the derivation of scalar, representative and homoskedastic measures of distance for the POLSAR data
  which is multidimensional, inter-correlated and heteroskedastic

Specifically, the following sub-objectives are to be achieved
\begin{enumerate}
\item                 To derive scalar and representative statistical models
                for the multi-dimensional and inter-correlated POLSAR
                data.
                \begin{enumerate}
                \item \label{itm:polsar_model} To derive a scalar statistical model for the
                POLSAR observable, being the determinant of the
                covariance matrix.
                \item \label{itm:polsar_discrimination_measure} To derive consistent discrimination measures for
                the observable being modelled 
                \item \label{itm:polsar_include_sar} To illustrate its representation power by showing
                that when the multi-channel POLSAR data is collapsed
                into the traditional one-channel SAR data, this
                determinant is transformed into the representative SAR
                intensity.
                \item \label{itm:polsar_validation} To validate the model against practical real-life
                captured POLSAR data.
                \item \label{itm:extend_sar_to_polsar} To demonstrate an example where an existing SAR
                processing technique is extensible towards POLSAR data
                \end{enumerate}
\item                To derive homoskedastic statistical models for the
                heteroskedastic (POL)SAR data. 
                \begin{enumerate}
                \item \label{itm:log_transform} To show that (POL)SAR data are heteroskedastic in
                the original domain and logarithmic transformation
                can convert this into a homoskedastic model.
                \item \label{itm:sar_measures_distance} To derive homoskedastic measures of distance for
                the multi dimensional POLSAR as well as for the one
                dimensional SAR data.
                \item \label{itm:sar_validation} To validate these statistical models against both
                practical SAR and POLSAR data
                \item To illustrate the beneficial applications of these
                statistical models. Specifically:
                \begin{enumerate}
                \item \label{itm:filter_vicious_circle} To show how the consistent sense of variance
                helps break the vicious cycle in the problem of SAR
                speckle filtering: a new statistical test for
                homogeneity and a new speckle filter is derived.
                \item \label{itm:log_mse} To show how the consistent sense of subtractive
                distance helps in the problem of evaluating (POL)SAR
                speckle filters: the log-MSE is proposed to combine the
                evaluation of radiometric preservation and speckle
                suppression power.
                \end{enumerate}
                \end{enumerate}
\end{enumerate}

@@

\section{Organisation of the Thesis}
The rest of this thesis is organized into five chapters, as follows:
The next chapter will survey the related publications
  and state-of-the-art techniques in modelling, processing, filtering and evaluating (POL)SAR speckle filter will be presented.
It will also discuss the different measures of distance for both SAR and POLSAR data, together with their extensive applications. 
Through these discussions, the need for a homoskedastic and scalar model for the multivariate and heteroskedastic POLSAR is brought forward.

@@

 The
                beneficial applications of these models is presented in
                chapter \ref{chap:applications}, where the property of a consistent sense of variance
                 helps to break the vicious cycle in SAR
                speckle filtering (Research Contribution \ref{itm:filter_vicious_circle}).
It
                also shows how MSE can again be applicable in the
                additive and homoskedastic domain to evaluate SAR
                speckle filters (Research Contribution \ref{itm:log_mse}).
An
                example of extending existing techniques from SAR to
                POLSAR is also demonstrated in this chapter where the
                MSE evaluation criteria is also shown capable of
                evaluating POLSAR speckle filters (Research Contribution \ref{itm:extend_sar_to_polsar}).
Finally, the contribution of the thesis with respect to the research objectives and research impact is discussed in the concluding chapter \ref{chap:conclusions}.

### 2013-07-31 2/literature_review.tex
Final changes before submission to Alan???

This chapter 
reviews the published literature for SAR and POLSAR data processing.
Specifically, its first section describes the multi-dimensional and stochastic nature of the POLSAR data.
The second section then illustrates the different approaches that have been published to address the grand challenge of modelling, processing and ultimately understanding these types of data.

\section{The Stochastic and Multivariate Nature of POLSAR data}

@@

In the field of POLSAR, the Wishart distance is probably the most widely used, as part of the well-known Wishart classifier \cite{Lee_1999_TGRS}.
It is defined \cite{Lee_1994_IJRS_2299} as:
\begin{equation*}
  d(C_x,C_y) = \ln|C_y| + tr(C_xC_y^{-1})
\end{equation*},
where $tr(C)$ denotes the trace of the matrix C. 
As a measure of distance, its main disadvantage is that $d(C_y,C_y) = \ln|C_y| \neq 0$.

Recent works have suggested alternative dissimilarity measures including the symmetric and asymmetric refined Wishart distance \cite{Anfinsen_2007_ESA_POLINSAR},
\begin{align*}
  d(C_x,C_y) &= \frac{1}{2} tr(C_x^{-1}C_y + C_y^{-1}C_x) - d \\
    d(C_x,C_y) &= \ln|C_x| - \ln|C_y| + tr(C_xC_y^{-1}) - d
\end{align*}
the Bartlett distance \cite{Kersten_2005_TGRS_519},
  \begin{align*}
  d(C_x,C_y) &= 2 \ln |C_{x+y}| - \ln |C_x| - \ln |C_y| - 2d\ln2
  \end{align*}
the Bhattacharyya distance \cite{Lee_2011_IGARSS_3740},
\begin{equation*}
  r(C_x,C_y) = \frac{|C_x|^{1/2} |C_y|^{1/2}}{|(C_x+C_y)/2|}
\end{equation*}
and the Wishart Statistical test distance \cite{Cao_2007_TGRS_3454}
\begin{equation*}
  d(C_x,C_y) = (L_x + L_y) \ln|C| - L_x \ln|C_x| - L_y\ln|C_y|
\end{equation*}
.

@@

\subsection{Current Methods to Evaluate SAR Speckle Filters}

@@

In the next chapters, theoretical models are built to form the foundation required to systematically tackle these issues.

>>>>

This chapter 
reviews the published literature for SAR and POLSAR data processing.
Specifically, its first section describes the multi-dimensional and stochastic nature of the (POL)SAR data.
The second section then illustrates the different approaches that have been published to address the grand challenge of modelling, processing and ultimately understanding these types of data.

\section{The Stochastic and Multivariate Nature of (POL)SAR data}

@@

In the field of POLSAR, the Wishart distance is probably the most widely used, as part of the well-known Wishart classifier \cite{Lee_1999_TGRS}.
It is defined \cite{Lee_1994_IJRS_2299} as:
\begin{equation*}
  d(C_x,C_y) = \ln|C_y| + tr(C_xC_y^{-1})
\end{equation*}
where $tr(C)$ denotes the trace of the matrix C. 
As a measure of distance, its main disadvantage is that $d(C_y,C_y) = \ln|C_y| \neq 0$.

Recent works have suggested alternative dissimilarity measures including the symmetric and asymmetric refined Wishart distance \cite{Anfinsen_2007_ESA_POLINSAR},
\begin{align*}
  d(C_x,C_y) &= \frac{1}{2} tr(C_x^{-1}C_y + C_y^{-1}C_x) - d \\
    d(C_x,C_y) &= \ln|C_x| - \ln|C_y| + tr(C_xC_y^{-1}) - d
\end{align*}
the Bartlett distance \cite{Kersten_2005_TGRS_519},
  \begin{align*}
  d(C_x,C_y) &= 2 \ln |C_{x+y}| - \ln |C_x| - \ln |C_y| - 2d\ln2
  \end{align*}
the Bhattacharyya distance \cite{Lee_2011_IGARSS_3740},
\begin{equation*}
  r(C_x,C_y) = \frac{|C_x|^{1/2} |C_y|^{1/2}}{|(C_x+C_y)/2|}
\end{equation*}
and the Wishart Statistical test distance \cite{Cao_2007_TGRS_3454}
\begin{equation*}
  d(C_x,C_y) = (L_x + L_y) \ln|C| - L_x \ln|C_x| - L_y\ln|C_y|
\end{equation*}

@@

\subsection{Current Techniques to Evaluate SAR Speckle Filters}

@@

In the next chapter, theoretical models are developed to form the foundation required to systematically tackle these issues.
